Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Explain figure 3

In \cref{figure:ids} we show that this is useful in practice.

Some other forms do not translate. For example, another invariant which can be effective on regular
graphs is to count the number of neighbours of a vertex which are present in a triangle \cite{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot make use of this fact.

>>>>

In \cref{figure:ids} we show that this is effective in practice: we show the amount of domain reduction
we can achieve at the top of search by using invariants and a fixed $k$, compared to the search
space size for the maximum common induced subgraph problem. (The results on the non-induced version
show a similar but slightly weaker trend.)

Some other invariants do not translate. For example, another rule which can be effective on regular
graphs involves count the number of neighbours of a vertex which are present in a triangle
\cite{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot
make use of this fact.
